---
title: "Cabbages"
author: "Wayne Jarvis"
date: "Fall 2025"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

Yes, there is a significant difference in the amount of VitC between c39 and c52. We can see that c52 is much larger than c39, with the bottom of the box surpassing the top of c39's box. Thus, the average for c39 is much smaller than the average for c52.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We used numerical and categorical data to solve these problems. Using the helper file numerical cat rmd, we are able to see the various boxplots we need in order to be successful. The boxpolot was the graphical method and the numerical method was taking that data from the box and interpreting it.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

Our descriptive results show that c52 is much larger than c39. We can see that the average is higher, so even at its lowest, c52 is ahead of c39. With inference, we can make an educated guess that within the context of this problem, c52 will always be larger than c39, no matter which variable you are looking at.

## Descriptive Results

```{r}
boxplot(VitC~Cult,data=veggy)
```

This plot measures the amount of VitC dependent on the cultivation. The C52 box is higher than the top of the C39 box. This means that box C52 is significantly bigger than box C39.

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The Q3 for C39 has a value of 54.75 which is lower than the Q1 for C52. Normally, the result of Q3 being higher than that of Q1 means that they are significantly different. The probability of obtaining the other number is not likely. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
